problem years

### 2024-07-03 src/problem_years_old.Rmd
corrected RF v2 LA

library(tidyverse)
library(rprojroot)
library(plm)
library(sf)
library(magick)
library(ggrepel)
library(scales)

@@

```{r}
n = 1 #number of unique postcodes. 
m = 11

@@

@@

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n)             # for n == 1

df.long <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  #arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_1996, n_1999, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010, n_2011, n_2012) %>%
  arrange(desc(n_2004), desc(n_2005)) %>% 
  slice_head(n=1000) %>% 
  pivot_longer(!pc, names_to = "year", values_to = "n") %>% 
  mutate(year = as.integer(sub("n_", "", year, fixed = TRUE))) %>% 
  replace(is.na(.), 0) %>% 
  mutate(outlier = ifelse(n > 1000 & (year==2004 | year == 2005), pc, ""))

problem.pcs <- df.long %>% filter(year==2004 | year == 2005, 
                   n > 1000) %>% 
  distinct(pc)

# n > 1500: "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"   
# n > 1000: SE24 9HP, CV8 2ED, GL16 7YA, CW1 6GL, M28 2SL, DE21 7BF

df.long %>% 
  mutate(year = as.double(year)) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text_repel(aes(x = year, y = n, label=outlier), cex = 3)

path.out <- paste0(path, "/outputs/pc_year_1.png")
ggsave(path.out, bg='#ffffff')  
```

## Corrected

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df.corrected <- pdata.frame(df.corrected)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df.corrected), newdata = df.corrected), 2)

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]

df.corrected %>% 
  as_tibble() %>% 
  mutate(year = as.double(as.character(year))) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

path.out <- paste0(path, "/outputs/pc_year_1_corrected.png")
ggsave(path.out, bg='#ffffff')  
```

### LA df

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = n()) %>% # for multiple pc  
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/LA/morani_la_1.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

@@

### OA df

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>% # for multiple pc  
  ungroup() %>% 
  complete(oa11cd, year) %>% 
  filter(!is.na(oa11cd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/OA/morani_oa_1.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

>>>>

library(tidyverse)
library(rprojroot)
library(plm)
library(sf)
library(magick)
library(ggrepel)

@@

```{r}
n = 1 #number of unique postcodes. 
m = 12

@@

# df9610 %>% filter(V1.domain == 1) %>% 
#   left_join(lookup, by = "pc", suffix =c("","")) %>% 
#   filter(ladcd == "E08000006" & year == 2006) %>% 
#   group_by(pc) %>% 
#   summarise(n = n()) %>% 
#   arrange(desc(n))
# 
# df9610 %>% filter(pc == "M28 2SL" & year == 2006 & V1.domain == 1)

problem.pcs <- df9610 %>% filter(year > 1999 & year < 2011) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  # complete(pc, year) %>% 
  # replace(is.na(n), 0) %>% 
  arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010) %>% 
  slice_head(n=10) %>% 
  dplyr::select(pc)

# [1] "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"  "EC1V 4PY" "DE21 7BF" "E14 9SR"  "GL16 7YA" "WC1N 3XX"
# [10] "CB2 1AB" 
```

```{r}
df %>%  pivot_longer(!LSOA11CD, names_to = "time", values_to = "premises") %>% 
  left_join(look.up) %>%
  group_by(LAD22CD, time) %>% 
  summarise(premises = sum(premises)) %>% #ungroup() %>% filter(LAD22CD == 'E08000025')
  # group_by(LAD22CD) %>% 
  # mutate(help = mean(premises)) %>% 
  # filter(help<70) %>% 
  ggplot() +
  geom_line(mapping = aes(x = time, y = premises, group = LAD22CD), alpha = .3, size = .2) + #, color = 'Premises'
  #ggtitle("Median experienced internet speeds for Local Authorities") + 
  xlab("time") + ylab("Gambling premises") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

a <- df9610 %>% #filter(year > 1999 & year < 2011) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  #arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010) %>%
  arrange(desc(n_2004), desc(n_2005)) %>% 
  slice_head(n=1000) %>% 
  pivot_longer(!pc, names_to = "year", values_to = "n") %>% 
  mutate(year = as.integer(sub("n_", "", year, fixed = TRUE)))  
a %>% ggplot() +
  geom_line(mapping = aes(x = year, y =n, group = pc), alpha = .3, size = .2)
```

## Correct 1996-2010

```{r}
df9610 <- df9610 %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df9610 <- pdata.frame(df9610)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df9610), newdata = df9610), 2)

df9610$n[is.na(df9610$n)] <- predictions[is.na(df9610$n)]
df9610 %>% filter(pc == "M28 2SL") %>% distinct(year)
```

### Load remaining data

```{r}
df9610 <- as_tibble(df9610) %>% 
  mutate(year = as.double(as.character(year))) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>%
  group_by(year, ladcd) %>%
  summarise(n = n()) %>%            
  ungroup()

@@

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = n()) %>%             # for n == 1  
  #summarise(n = sum(V1.domain)) %>% # for multiple pc  
  ungroup()

df <- bind_rows(df9610, df1112) %>% 
  filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

# tests for Scotland
# df %>% filter(substr(oa11cd, 1,1) =="S",
#               year==2010) %>% summarise(mean(n, na.rm = T))
# 
# df %>% filter(oa11cd=="S00090182")
# 
# test@data %>% filter(substr(id, 1,1) =="S",
#                      n!=0)
# 
# df %>% filter(substr(oa11cd, 1,1) =="W",
#               year==2003)
```

@@

filename = paste(path.out, t, ".png", sep = "")
ggsave(filename)
}
```

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/LA/morani_la.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

@@

### Load remaining data

```{r}
df9610 <- as_tibble(df9610) %>% 
  mutate(year = as.double(as.character(year))) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>%
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%            
  ungroup()

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%             # for n == 1  
  #summarise(n = sum(V1.domain)) %>% # for multiple pc  
  ungroup()

df <- bind_rows(df9610, df1112) %>% 
  filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

# tests for Scotland
# df %>% filter(substr(oa11cd, 1,1) =="S",
#               year==2010) %>% summarise(mean(n, na.rm = T))
# 
# df %>% filter(oa11cd=="S00090182")
# 
# test@data %>% filter(substr(id, 1,1) =="S",
#                      n!=0)
# 
# df %>% filter(substr(oa11cd, 1,1) =="W",
#               year==2003)
```

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/OA/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable() %>% 
  write_csv(path.out)
```
